\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex

%%%%%%%%%%%%%
\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases for MR10 fixed vs. adaptive mesh}}

\medskip
\KCnote{ 4regions and 4 permeabilities}
\noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. There is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}) so the next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh test case. Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of th esimulation for different time-steps as these are desrcibed. In this set the interfacial instability is becoming more profound. Based on these two case so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.

>>>>

%%%%%%%%%%%%%
\subsection{\blue{need to find a name for this heterogeneous region/set of test-cases for MR10 fixed vs. adaptive mesh}}

\medskip
\KCnote{ 4regions and 4 permeabilities}
\noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Initial and boundary conditions are described in fig. \ref{fig:testcase_heter_domain}. What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}). The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh. %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. 
Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described. In this set the interfacial instability is becoming more profound as the flow develops. Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
